Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex

\section{Implementation}

@@

\subsection{Implementation Details}

@@

@@

\subsubsection{Component 2}

\subsubsection{Component 3}

>>>>

\section{Design}

@@

\section{Implementation Details}

@@

\subsection{Game ({\secit Kimbee})}

The Game is the system that the children interact with to practice speech. Since this system also performs speech processing to determine speech correctness, there are many interacting components. From a high level, the major sub systems are: the Phaser Game Implementation, the Speech Processing System, and the Server Application Programming Interface (API). We target this project toward web technologies to allow wide distribution and adoption. From a design standpoint, we strived to make each system loosely connected and non-disruptive to gameplay. This required us to explore various new web technologies including Webworkers for multithreading and the UserMedia HTML5 API.

\subsubsection{Platform choice}
Since we want this project to work on as many devices as possible, we target emerging web technologies that work seamlessly across all devices with a web browser component. The web technology stack is advanced enough to handle our needs: there is a JavaScript port of the popular speech processing library CMU Sphinx, and we now have access to the user's microphone via UserMedia HTML5 API. After creating our project in the browser, we then can translate it to native applications via Apache Cordova, a web distribution technology based on embeddeding a web component inside a native application container on mobile devices.

\subsubsection{Phaser Game Implementation}
The Game component of the Kimbee system encompasses the view and control of the application: The main menu, the game play, and rendering. This is what the children interact with to practice speech. The game is implemented with the Phaser Game Framework. Which represents screens of the game into states. States are linked together in meaningful ways. For example, the Main Menu State links to the Option Menu State via a Phaser Framework Button. It also provides image animation, tweening, and collision support. To create our microphone button, we extend the Phaser Framework Button and implement connections to the speech processing component while preserving button functionality through inheritance.

\subsection{Therapist Portal}

[High Level Overview of Therapist Portal (tech)]

@@
